A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-04 latex/main.tex
Updates from Overleaf

In the ARG, XR, XU, XAA, XAG, and XAM
are nested under the XQ recombinant lineage.
However, upon closer inspection,
the right hand branch above the recombination node appears problematic,
as it displays three reversion mutations,
which revert mutations at positions 22792, 24023, and 25624
in the ancestral lineage just above.
These sites were excluded during ARG inference, and
remapped onto the ARG by parsimony during ARG postprocessing.
If these three sites were used during primary ARG inference,
the right parent of the recombination node
may have been chosen to be the ancestral BA.2 sample
on the right-hand path with 18 child nodes.
A more parsimonious reconstruction
would then have the XQ clade as a sibling to
a group of (monophyletic) XAA, XAM, XAG, and XR lineages.
This would remove between 4 and 5 reversion mutations.

>>>>

In the ARG, XR, XU, XAA, XAG, and XAM
are nested under the XQ recombinant lineage.
These lineages were designated around the same time,
roughly within a five-month period (Mar. to Jul., 2022).
Also, their breakpoint intervals of these lineages,
as suggested in the Pango designation issues,
all occur at the 5' end of the genome
within a $\sim$5,000 base segment ($\sim$4,300 to $\sim$9,400).

Upon closer inspection,
the right-hand branch above the recombination node appears problematic,
as it displays three reversion mutations,
which revert mutations at positions 22792, 24023, and 25624
in the ancestral lineage just above.
These sites were excluded during ARG inference, and
remapped onto the ARG by parsimony during ARG postprocessing.
If these three sites were used during primary ARG inference,
the right parent of the recombination node
may have been chosen to be the ancestral BA.2 sample
on the right-hand path with 18 child nodes.
A more parsimonious reconstruction
would then have the XQ clade as a sibling to
a group of (monophyletic) XAA, XAM, XAG, and XR lineages.
This would remove between 4 and 5 reversion mutations.
